Notes on 10d Super Yang-Mills

### 2019-03-21 10d_SYM_Notes.tex
Added comments on Baulieu's scalar supersymmetry
added a remark on scalar SUSY without h

Consider the following square-zero supersymmetry acting on Baulieu's theory:
\begin{align*}
\delta A_{1,0} &= \psi \\
\delta \chi &= h \\
\delta B &= F_{0,2} \\
\end{align*}
acting trivially on all other (BRST) fields.  This clearly squares to zero, so defines an action of the supergroup $\Pi \CC$ on the BRST complex.  We can calculate the variation of the action functional with respect to this symmetry, and see that it vanishes.  Indeed,
\begin{align*}
\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
&= \int \langle J^2(\dd_{A_{1,0}} B \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge (\dd_{A_{1,0}} \psi) - 0) \Omega \rangle \\
&= 0.
\end{align*}
This should mean that the $\Pi \CC$ action is off-shell, so extends to an action on the full BV complex (the above calculation should be equivalent to showing that $\delta$ commutes with the BV differential).

>>>>

Consider the following square-zero supersymmetry acting on Baulieu's theory:
\begin{align*}
\delta A_{1,0} &= \psi \\
\delta \chi &= h \\
\delta B &= F_{0,2} \\
\end{align*}
acting trivially on all other (BRST) fields.  This clearly squares to zero, so defines an action of the supergroup $\Pi \CC$ on the BRST complex.  We can calculate the variation of the action functional with respect to this symmetry, and see that it vanishes.  Indeed,
\begin{align*}
\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
&= \int \langle J^2(\dd_{A_{1,0}} \psi \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge \dd_{A_{1,0}} \psi)\Omega - 0\rangle \\
&= 0.
\end{align*}
This should mean that the $\Pi \CC$ action is off-shell, so extends to an action on the full BV complex (the above calculation should be equivalent to showing that $\delta$ commutes with the BV differential).

Let me also explicitly show that the BV action functional is also invariant for this square-zero supersymmetry.  So we also include the dual action
\begin{align*}
\delta \psi^* &= A_{1,0}^* \\
\delta h^* &= \chi^* \\
\delta A_{0,1}^* &= \ol \dd_{A_{0,1}} B^*.
\end{align*}
The variation of the part of the BV action functional involving the anti-fields is then calculated to vanish as follows.
\begin{align*}
&\!\!\! \delta S_{\mr{anti}} = \\
&= \int \delta \left(c^* \wedge [c, c] + {A^*_{1, 0}}\wedge (\partial c + [c,A_{1,0}]) + {A^*_{0, 1}}\wedge (\ol \dd c + [c, A_{0, 1}]) - B^*\wedge [c, B] - \chi^*\wedge [c, \chi] - \psi^*\wedge [c, \psi] \right) + h^* \wedge [c,h] \\
&= \int 0 +A^*_{1,0} \wedge [c,\psi] + \ol \dd_{A_{0,1}} B^* \wedge [c,A_{0,1}] - B^* \wedge [c,F_{0,2}] - \chi^* \wedge [c,h] - A_{1,0}^* \wedge [c,\psi] + \chi^* \wedge [c,h] \\
&= 0.
\end{align*}

\begin{remark}
If we don't adjoin the auxiliary field $h$, but do break the $\spin(10)$ symmetry down to $\SU(5)$ and consider the scalar supersymmetry with respect to the on-shell action from the previous section, then the BRST action is still preserved.  The supersymmetries are as above, except that now $\delta \chi = JF_{1,1)}$.  We have, very similarly to the calculation above,
\begin{align*}
\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega + J^2(F_{1,1}^2) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
&= \int \langle J^2(\dd_{A_{1,0}} \psi \wedge F_{0,2})\Omega - 0 + J^2(F_{1,1} \wedge \ol \dd_{A_{0,1}} \psi) \Omega - J^2( F_{1,1} \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge \dd_{A_{1,0}} \psi)\Omega - 0 \rangle \\
&= 0.
\end{align*}
\chris{Actually maybe this doesn't quite work, because of a factor of two.  We had $\delta(hJF_{1,1}) = hJ(\ol \dd \psi)$, whereas $\delta(J^2F_{1,1}^2) = 2 J^2(F_{1,1} \wedge \ol \dd \psi)$, and that extra 2 seems to break the cancellation.}

On the other hand, if try to extend this to the BV fields, we must have $\delta A^*_{1,0} = 0$ so that $\delta^2 = 0$, so we would need to modify $\delta A^*_{0,1}$ to include some term cancelling the term $\delta(\chi^*\wedge [c, \chi]) = \chi^* \wedge [c, JF_{1,1}]$, but without introducing a new term $\delta(A_{0,1}^* \wedge \ol \dd c)$.  This na\"ively doesn't look like it's possible.

\end{remark}
